Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{equation} \label{chapter5:eq4}
  C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
\end{equation}
$|K|$ represents the number of symbols in $K$.

@@

Figure~\ref{fig:channel}(b) shows the example of the type of the channel. Once the input symbol is determined, the output symbol is also determined. As we can see, the channel has a unique output ($o \in O$) for every input ($k \in K$).

@@

We consider an attacker who shares the same hardware resource with the victim. The attacker may not know the memory access the victim program accesses directly. Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program. We call the memory access information as the observation ($O$) in the rest of the chapter. This is a typical scenario for most side-channel attacks.  We also assume the attacker can have access to the source code of the victim program ($\beta$). It is a valid assumption since most side-channel attacks target open-source software. Also, like recent works, we assume the attacker has a noise-free observation. For some side-channel channels like the controlled-channel attacks, it is already true. The program ($\beta$) has $K$ as the sensitive input. $K$ is a finite set that consists of every possible key ($k \in K$). The program also takes known messages $M$ as the input.

>>>>

\begin{equation} \label{chapter5:eq4}
  C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
\end{equation}
$|K|$ represents the number of possible variables in $K$.

@@

Figure~\ref{fig:channel}(b) shows the example of the type of the channel. Once the input symbol is determined, the output symbol is also determined. Shown in Figure~\ref{fig:channel}(b), the channel has the unique output ($o \in O$) for every input ($k \in K$).

@@

We consider an access-based attack~\cite{DBLP:journals/jce/GeYCH18}, where an adversary can probe one time for each run only after the termination of a deterministic program. The attacker may not know the memory access the victim program accesses directly. Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program. We call the memory access information as the observation ($O$) in the rest of the paper. It is a typical scenario for most side-channel attacks.  We also assume the attacker can have access to the source code of the victim program ($\beta$). It is a valid assumption since most side-channel attacks target open-source software. Also, like recent works, we assume the attacker has a noise-free observation. For some side-channel channels like the controlled-channel attacks, it is already true. The program ($\beta$) has $K$ as the sensitive input. $K$ is a finite set that consists of every possible key ($k \in K$). The program also takes known messages $M$ as the input.
